Efficient Selection of Time Series Shapelets

### 2024-04-19 Docs/paper/main.tex
Some minor changes

\subsection{Similarity search indexing-based shapelets}
In the previous subsection, we have used clustering to get rid of the evaluation
part and reduce the computational overhead. However, we used clustering because
it is the first intuitive step that comes in order to optimize for the 
silhouette score.
Since what we care about is the structure of similarity search, i.e., we want to
know, for each subsequence, which other subsequences are the most similar. To
answer these questions, one can use efficient indexing data structures from the
nearest-neighbor problem literature, which is more efficient compared to 
clustering in terms of time complexity and running time.

>>>>

\subsection{Similarity search indexing-based shapelets}
In the previous subsection, we have used clustering to get rid of the evaluation
part and reduce the computational overhead. We used clustering because it is the
first intuitive idea in order to optimize for the silhouette score.
Since what we care about is the structure of similarity search, i.e., we want to
know, for each subsequence, which other subsequences are the most similar. An
alternative approach to answer these questions, one can use efficient indexing
data structures from the nearest-neighbor problem literature, which is more 
efficient compared to clustering in terms of time complexity and running time.
